---
title: "Main Analysis"
output: html_notebook
---

This notebook is the main analysis code for the economic part of the thesis. It takes the analysis-ready data generated in the file "econ_5_dataset_creation.Rmd" and runs Difference-in-Differences and Event Study estimators on it.

## Setup

```{r message=FALSE, warning=FALSE, include=FALSE}
set.seed(42)

options(scipen=999)

library(tidyverse)
library(xtable)
library(fixest)
library(lubridate)
library(sf)
library(spdep)

dataDir <- "C:/Users/Kamal/OneDrive/TSE/M2 EE/thesis/econ/data/"
graphDir <- "C:/Users/Kamal/OneDrive/TSE/M2 EE/thesis/econ/graphics/"

data <- st_read(paste0(dataDir,"ard_luz_clim_full.shp"))

IHS <- function(x){log(x+(x^2+1)^(1/2))}
```

## Initial Data Wrangling

This creates an first version of the final data set:

```{r}
estim_data_full <- data %>% 
  mutate(area_ha = as.numeric(st_area(.))/10000) %>%
  data.frame() %>% 
  select(-geometry) %>% 
  filter(!is.na(mintemp)) %>% 
  pivot_wider(names_from = year, values_from = c(prevcover,loss,mintemp)) %>% 
  filter(prevcover_2001 != 0) %>% 
  pivot_longer(starts_with(c("prevcover","loss","mintemp")), names_to = c("variable","year"), 
               names_sep = "_", values_to = "value") %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  relocate(year,prevcover,loss,mintemp, .after = id) %>% 
  filter(!is.na(prevcover)) %>% 
  filter(!is.na(loss))

```


## Descriptive Stats

Here is a table that gives some insights into the estimation data.

```{r eval=FALSE, include=FALSE}

stats <- rbind(
  
  # number of cells (total)
  estim_data_full %>% select(id,type) %>% distinct() %>% count(type) %>% arrange(type)%>%pull(n),
  
  #number of different sites (total) 
  estim_data_full %>% select(zone,type) %>% distinct() %>% count(type) %>% arrange(type) %>% pull(n),
  
  # total area (ha)
  estim_data_full %>% select(id,type,area_ha) %>% distinct() %>% 
    summarize(area_ha = sum(area_ha, na.rm = T), .by = type) %>% arrange(type) %>% pull(area_ha),
  
  # mean area(ha) per cell
  estim_data_full %>% select(id,type,area_ha) %>% distinct() %>% 
    summarize(area_ha = mean(area_ha, na.rm = T), .by = type) %>% arrange(type) %>% pull(area_ha),
  
  # mean forest cover % in 2001
  estim_data_full %>% filter(year == 2001) %>% select(id,type,prevcover,area_ha) %>% 
    summarize(weighted_cover = mean(prevcover*100/area_ha, na.rm = T), .by = type) %>% 
    arrange(type)%>% pull(weighted_cover),
  
  # mean forest cover % in 2021
  estim_data_full %>% filter(year == 2021) %>% select(id,type,prevcover,area_ha) %>% 
    summarize(weighted_cover = mean(prevcover*100/area_ha, na.rm = T), .by = type) %>% 
    arrange(type)%>% pull(weighted_cover),
  
  # mean loss (% of forest area)
  estim_data_full %>% select(id,type,loss,prevcover) %>% 
    summarize(weighted_loss = mean(loss*100/prevcover, na.rm = T), .by = type) %>% arrange(type) %>%
    pull(weighted_loss),
  
  # mean mintemp (°C)
  estim_data_full %>% select(id, type, mintemp) %>% 
    summarize(mintemp = mean(mintemp, na.rm = T), .by = type) %>% arrange(type) %>% pull(mintemp)

)
  

land_use_zones <- c("BMTA", "Conservancy", "Other coastal BC", "Ecological Reserve", 
                    "Other GBR", "Provincial Park", "SFMA")

statnames <- c("Number of cells", "Number of sites", "Total area (ha)", "Mean area (ha)", 
               "Mean forest cover (% of area) in 2001",
               "Mean forest cover (% of area) in 2021",
               "Mean loss (% of forest cover)",
               "Mean yearly minimum temperature (°C)")

rownames(stats) <- statnames
colnames(stats) <- land_use_zones

xtable(stats)

```

## Aggregated Time Series/Parallel Trends

What I want to show here is the yearly time series of forest loss (as a percentage of forest cover) aggregated on a land-use-type level. This produces Figure 3 in the paper.


```{r}
control_vector <- estim_data_full %>%
  mutate(weighted_loss = loss*100/prevcover) %>%
  summarize(weighted_loss = mean(weighted_loss, na.rm = T), .by = c(year,type, gbr)) %>% 
  filter(type == "Control") %>% 
  pull(weighted_loss)


estim_data_full %>%  
  filter(type != "Control") %>%
  mutate(year = as.Date(as.character(year), format = "%Y")) %>%
  mutate(weighted_loss = loss*100/prevcover) %>%
  summarize(Treatment = mean(weighted_loss, na.rm = T), .by = c(year,type)) %>% 
  mutate(Control = rep(control_vector,6)) %>%
  pivot_longer(3:4, names_to = "Treatment", values_to = "weighted_loss")%>% 
  ggplot() +
    geom_line(aes(x = year, y = weighted_loss, color = Treatment)) +
    geom_vline(aes(xintercept = as.Date("2006", format = "%Y")), linetype = "dashed") +
    geom_vline(aes(xintercept = as.Date("2017", format = "%Y")), linetype = "dashed") +
    facet_wrap(~type, scales = "free_y", ncol = 3) +
    labs(x = "Year", y = "Forest loss (% of forest cover)") +
    scale_color_manual(name = "", values = c("orange", "dodgerblue3")) +
    theme_bw()

#ggsave("C:/Users/Kamal/OneDrive/TSE/M2 EE/thesis/econ/graphics/parallel_trends_full.png", width = 8, height = 4)
```

The next chunks explore the visible spikes in the Provincial Parks. This first shows that the spikes come from Tweedsmuir Park in particular:

```{r}
estim_data_full %>% 
  filter(type == "Provincial Park") %>% 
  filter(year %in% c(2004,2009,2019)) %>% 
  arrange(desc(loss))
```

Here, we plot the winter temperature by land use zone to see whether the spikes correlate with the previous graph. This is Figure 4 in the paper.

```{r}
estim_data_full %>% 
  mutate(year = as.Date(as.character(year), format = "%Y")) %>%
  summarize(mintemp = mean(mintemp,na.rm = T), .by = c(year,type)) %>% 
  ggplot() +
    geom_line(aes(x = year, y = mintemp, color = type)) +
    scale_color_viridis_d(name = "Land Use Zone", option = "cividis", direction = -1) +
    labs(x = "Year", y= "Minimum temperature (°C) in preceding winter") +
    theme_bw()

#ggsave("graphics/temp_check.png", width = 8, height = 4)
```



## Estimation

This section details different estimations.

### Global estimations

First, I'll designate the entirety of the GBR as treatment, and the rest of the coast as control. I'll run an event study with the cutoff in 2006, and one with the cutoff in 2017 to check for parallel trends. In the 2006 version, the data runs until 2016 (before the GBRFMA), in the 2017 version, the data starts in 2010 (after the last big amendment to the agreements. In doing so, I'm creating data sets with leads and lags centered around the cutoffs that I can reuse down below.

Event Study for 2006:

```{r}
estim_data_all_2006 <- estim_data_full %>% 
  filter(!type %in% c("Ecological Reserve", "Provincial Park")) %>% 
  mutate(year = as.numeric(year)) %>% 
  filter(year < 2017) %>% 
  mutate(post_2006 = ifelse(year >= 2006,1,0)) %>% 
  mutate(timetil_2006 = year - 2006) %>% 
  mutate(lead1 = case_when(timetil_2006 == -1 ~ 1, TRUE ~ 0),
    lead2 = case_when(timetil_2006 == -2 ~ 1, TRUE ~ 0),
    lead3 = case_when(timetil_2006 == -3 ~ 1, TRUE ~ 0),
    lead4 = case_when(timetil_2006 == -4 ~ 1, TRUE ~ 0),
    lead5 = case_when(timetil_2006 == -5 ~ 1, TRUE ~ 0),
    lag0 = case_when(timetil_2006 == 0 ~ 1, TRUE ~ 0),
    lag1 = case_when(timetil_2006 == 1 ~ 1, TRUE ~ 0),
    lag2 = case_when(timetil_2006 == 2 ~ 1, TRUE ~ 0),
    lag3 = case_when(timetil_2006 == 3 ~ 1, TRUE ~ 0),
    lag4 = case_when(timetil_2006 == 4 ~ 1, TRUE ~ 0),
    lag5 = case_when(timetil_2006 == 5 ~ 1, TRUE ~ 0),
    lag6 = case_when(timetil_2006 == 6 ~ 1, TRUE ~ 0),
    lag7 = case_when(timetil_2006 == 7 ~ 1, TRUE ~ 0),
    lag8 = case_when(timetil_2006 == 8 ~ 1, TRUE ~ 0),
    lag9 = case_when(timetil_2006 == 9 ~ 1, TRUE ~ 0),
    lag10 = case_when(timetil_2006 == 10 ~ 1, TRUE ~ 0))


event_all_2006 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lag0 + lag1 + lag2 + lag3 + lag4 + 
                                           lag5 + lag6 + lag7 + lag8 + lag9 + lag10) + mintemp | 
                          id + year + region, 
                          data = estim_data_all_2006, 
                          panel.id = ~id+year,
                          weights = ~prevcover, 
                          cluster = ~region)



years_2006 <- 2001:2016
coefficient_lead_names_2006 <- c("gbr:lead5","gbr:lead4", "gbr:lead3","gbr:lead2")

coefficient_lag_names_2006 <- c("gbr:lag0", "gbr:lag1","gbr:lag2","gbr:lag3","gbr:lag4","gbr:lag5","gbr:lag6",
                                "gbr:lag7","gbr:lag8","gbr:lag9","gbr:lag10")


data.frame(cbind(years_2006,
                 c(summary(event_all_2006)$coefficients[coefficient_lead_names_2006],0,
                       summary(event_all_2006)$coefficients[coefficient_lag_names_2006]), 
                 c(summary(event_all_2006)$se[coefficient_lead_names_2006],0,
                       summary(event_all_2006)$se[coefficient_lag_names_2006]))) %>% 
  rename(Year = years_2006, Coefficient = V2, STE = V3) %>% 
  mutate(Upper = Coefficient + qnorm(0.975)*STE, Lower = Coefficient - qnorm(0.975)*STE) %>% 
  mutate(Year = as.Date(paste0(as.character(Year),"-01-01"), format = "%Y-%m-%d")) %>% 
  ggplot(aes(x = Year, y = Coefficient)) +
    geom_point(color = "darkslateblue") +
    geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "darkslateblue") +
    geom_hline(aes(yintercept = 0)) +
    geom_vline(aes(xintercept = as.Date("2005-11-01", format = "%Y-%m-%d")), linetype = "dashed")


```

This renders a global DiD analysis with the cutoff in 2006 invalid, as parallel trends are violated. 

Event study for 2017 (this produces Figure 5):

```{r}
estim_data_all_2017 <- estim_data_full %>% 
  filter(!type %in% c("Ecological Reserve", "Provincial Park")) %>% 
  mutate(year = as.numeric(year)) %>% 
  mutate(post_2017 = ifelse(year >= 2017,1,0)) %>% 
  filter(year > 2009) %>% 
  mutate(timetil_2017 = year - 2017) %>% 
  mutate(lead1 = case_when(timetil_2017 == -1 ~ 1, TRUE ~ 0),
    lead2 = case_when(timetil_2017 == -2 ~ 1, TRUE ~ 0),
    lead3 = case_when(timetil_2017 == -3 ~ 1, TRUE ~ 0),
    lead4 = case_when(timetil_2017 == -4 ~ 1, TRUE ~ 0),
    lead5 = case_when(timetil_2017 == -5 ~ 1, TRUE ~ 0),
    lead6 = case_when(timetil_2017 == -6 ~ 1, TRUE ~ 0),
    lead7 = case_when(timetil_2017 == -7 ~ 1, TRUE ~ 0),
    lag0 = case_when(timetil_2017 == 0 ~ 1, TRUE ~ 0),
    lag1 = case_when(timetil_2017 == 1 ~ 1, TRUE ~ 0),
    lag2 = case_when(timetil_2017 == 2 ~ 1, TRUE ~ 0),
    lag3 = case_when(timetil_2017 == 3 ~ 1, TRUE ~ 0),
    lag4 = case_when(timetil_2017 == 4 ~ 1, TRUE ~ 0))


event_all_2017 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lead6 + lead7 + lag0 + lag1 + 
                                           lag2 + lag3 + lag4) + mintemp | id + year + region, 
                      data = estim_data_all_2017, 
                      panel.id = ~id+year,
                      weights = ~prevcover, 
                      cluster = ~region)

years_2017 <- 2010:2021

coefficient_lead_names_2017 <- c("gbr:lead7", "gbr:lead6", "gbr:lead5","gbr:lead4", "gbr:lead3","gbr:lead2")

coefficient_lag_names_2017 <- c("gbr:lag0", "gbr:lag1","gbr:lag2","gbr:lag3","gbr:lag4")

data.frame(cbind(years_2017,
                 c(summary(event_all_2017)$coefficients[coefficient_lead_names_2017],0,
                       summary(event_all_2017)$coefficients[coefficient_lag_names_2017]), 
                 c(summary(event_all_2017)$se[coefficient_lead_names_2017],0,
                       summary(event_all_2017)$se[coefficient_lag_names_2017]))) %>% 
  rename(Year = years_2017, Coefficient = V2, STE = V3) %>% 
  mutate(Upper = Coefficient + qnorm(0.975)*STE, Lower = Coefficient - qnorm(0.975)*STE) %>% 
  mutate(Year = as.Date(paste0(as.character(Year),"-01-01"), format = "%Y-%m-%d")) %>% 
  ggplot(aes(x = Year, y = Coefficient)) +
    geom_point(color = "orange2") +
    geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "orange2") +
    geom_hline(aes(yintercept = 0)) +
    geom_vline(aes(xintercept = as.Date("2016-11-01", format = "%Y-%m-%d")), linetype = "dashed") +
    theme_bw()


#ggsave("graphics/event_2017_all.png", height = 4, width = 8)
```

This validates parallel trends, but also makes an effect in the DiD seem unlikely. Here is the DiD (results are mentioned in the text):

```{r message=FALSE, warning=FALSE}
did_all_2017 <- feols(IHS(loss) ~ gbr*post_2017 + mintemp | id + year + region, 
                      data = estim_data_all_2017, 
                      panel.id = ~id+year,
                      weights = ~prevcover, 
                      cluster = ~region)

summary(did_all_2017)
```



### Decomposition into different areas.


Undesignated areas - Event Study 2006:

```{r message=FALSE, warning=FALSE}
estim_data_non_2006 <- estim_data_all_2006 %>% filter(type %in% c("Control", "GBR - Not designated"))

event_non_2006 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lag0 + lag1 + lag2 + lag3 + lag4 + 
                                           lag5 + lag6 + lag7 + lag8 + lag9 + lag10) + mintemp | 
                          id + year + region, 
                          data = estim_data_non_2006, 
                          panel.id = ~id+year,
                          weights = ~prevcover, 
                          cluster = ~region)


data.frame(cbind(years_2006,
                 c(summary(event_non_2006)$coefficients[coefficient_lead_names_2006],0,
                       summary(event_non_2006)$coefficients[coefficient_lag_names_2006]), 
                 c(summary(event_non_2006)$se[coefficient_lead_names_2006],0,
                       summary(event_non_2006)$se[coefficient_lag_names_2006]))) %>% 
  rename(Year = years_2006, Coefficient = V2, STE = V3) %>% 
  mutate(Upper = Coefficient + qnorm(0.975)*STE, Lower = Coefficient - qnorm(0.975)*STE) %>% 
  mutate(Year = as.Date(paste0(as.character(Year),"-01-01"), format = "%Y-%m-%d")) %>% 
  ggplot(aes(x = Year, y = Coefficient)) +
    geom_point(color = "darkslateblue") +
    geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "darkslateblue") +
    geom_hline(aes(yintercept = 0)) +
    geom_vline(aes(xintercept = as.Date("2005-11-01", format = "%Y-%m-%d")), linetype = "dashed")

```

Again, no parallel trends.

Undesignated areas - Event Study 2017 (produces Figure 6):

```{r}
estim_data_non_2017 <- estim_data_all_2017 %>% filter(type %in% c("Control", "GBR - Not designated"))


event_non_2017 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lead6 + lead7 + lag0 + lag1 + 
                                           lag2 + lag3 + lag4) + mintemp | id + year + region, 
                      data = estim_data_non_2017, 
                      panel.id = ~id+year,
                      weights = ~prevcover, 
                      cluster = ~region)


data.frame(cbind(years_2017,
                 c(summary(event_non_2017)$coefficients[coefficient_lead_names_2017],0,
                       summary(event_non_2017)$coefficients[coefficient_lag_names_2017]), 
                 c(summary(event_non_2017)$se[coefficient_lead_names_2017],0,
                       summary(event_non_2017)$se[coefficient_lag_names_2017]))) %>% 
  rename(Year = years_2017, Coefficient = V2, STE = V3) %>% 
  mutate(Upper = Coefficient + qnorm(0.975)*STE, Lower = Coefficient - qnorm(0.975)*STE) %>% 
  mutate(Year = as.Date(paste0(as.character(Year),"-01-01"), format = "%Y-%m-%d")) %>% 
  ggplot(aes(x = Year, y = Coefficient)) +
    geom_point(color = "orange2") +
    geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "orange2") +
    geom_hline(aes(yintercept = 0)) +
    geom_vline(aes(xintercept = as.Date("2016-11-01", format = "%Y-%m-%d")), linetype = "dashed") +
    theme_bw()


#ggsave("graphics/event_2017_non.png", height = 4, width = 8)
```

Parallel trends are valid, but an effect in DiD unlikely. Here is the DiD (results mentioned in the paper):


```{r message=FALSE, warning=FALSE}
did_non_2017 <- feols(IHS(loss) ~ gbr*post_2017 + mintemp | id + year + region, 
                      data = estim_data_non_2017, 
                      panel.id = ~id+year,
                      weights = ~prevcover, 
                      cluster = ~region)

summary(did_non_2017)
```

Conservancies - Event Study 2006:

```{r message=FALSE, warning=FALSE}
estim_data_cons_2006 <- estim_data_all_2006 %>% filter(type %in% c("Control", "Conservancy"))

event_cons_2006 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lag0 + lag1 + lag2 + lag3 + lag4 + 
                                           lag5 + lag6 + lag7 + lag8 + lag9 + lag10) + mintemp | 
                          id + year + region, 
                          data = estim_data_cons_2006, 
                          panel.id = ~id+year,
                          weights = ~prevcover, 
                          cluster = ~region)


data.frame(cbind(years_2006,
                 c(summary(event_cons_2006)$coefficients[coefficient_lead_names_2006],0,
                       summary(event_cons_2006)$coefficients[coefficient_lag_names_2006]), 
                 c(summary(event_cons_2006)$se[coefficient_lead_names_2006],0,
                       summary(event_cons_2006)$se[coefficient_lag_names_2006]))) %>% 
  rename(Year = years_2006, Coefficient = V2, STE = V3) %>% 
  mutate(Upper = Coefficient + qnorm(0.975)*STE, Lower = Coefficient - qnorm(0.975)*STE) %>% 
  mutate(Year = as.Date(paste0(as.character(Year),"-01-01"), format = "%Y-%m-%d")) %>% 
  ggplot(aes(x = Year, y = Coefficient)) +
    geom_point(color = "darkslateblue") +
    geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "darkslateblue") +
    geom_hline(aes(yintercept = 0)) +
    geom_vline(aes(xintercept = as.Date("2005-11-01", format = "%Y-%m-%d")), linetype = "dashed")

```

No parallel trends.

Conservancies - Event Study 2017:


```{r}
estim_data_cons_2017 <- estim_data_all_2017 %>% filter(type %in% c("Control", "Conservancy"))


event_cons_2017 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lead6 + lead7 + lag0 + lag1 + 
                                           lag2 + lag3 + lag4) + mintemp | id + year + region, 
                      data = estim_data_cons_2017, 
                      panel.id = ~id+year,
                      weights = ~prevcover, 
                      cluster = ~region)


data.frame(cbind(years_2017,
                 c(summary(event_cons_2017)$coefficients[coefficient_lead_names_2017],0,
                       summary(event_cons_2017)$coefficients[coefficient_lag_names_2017]), 
                 c(summary(event_cons_2017)$se[coefficient_lead_names_2017],0,
                       summary(event_cons_2017)$se[coefficient_lag_names_2017]))) %>% 
  rename(Year = years_2017, Coefficient = V2, STE = V3) %>% 
  mutate(Upper = Coefficient + qnorm(0.975)*STE, Lower = Coefficient - qnorm(0.975)*STE) %>% 
  mutate(Year = as.Date(paste0(as.character(Year),"-01-01"), format = "%Y-%m-%d")) %>% 
  ggplot(aes(x = Year, y = Coefficient)) +
    geom_point(color = "darkslateblue") +
    geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "darkslateblue") +
    geom_hline(aes(yintercept = 0)) +
    geom_vline(aes(xintercept = as.Date("2016-11-01", format = "%Y-%m-%d")), linetype = "dashed")

```

Parallel trends, likely no effect. DiD:

```{r message=FALSE, warning=FALSE}
did_cons_2017 <- feols(IHS(loss) ~ gbr*post_2017 + mintemp | id + year + region, 
                      data = estim_data_cons_2017, 
                      panel.id = ~id+year,
                      weights = ~prevcover, 
                      cluster = ~region)

summary(did_cons_2017)
```


BMTAs/SFMAs with Fisher permutation test:

Placebo samples:

```{r message=FALSE, warning=FALSE}
sample_size <- 23

placebo_ids <- estim_data_all_2006 %>% 
  filter(gbr == 0) %>% select(id) %>% distinct() %>% pull(id)

placebo_samples <- data.frame(matrix(nrow = sample_size))

i <- 1

while(length(placebo_ids) >= sample_size){
  
  sample <- sample(placebo_ids, size= sample_size, replace =F)
  
  placebo_samples[,i] <- sample
  
  placebo_ids <- placebo_ids[!placebo_ids %in% sample]
  
  i <- i +1

}

placebo_samples <- cbind(placebo_samples, append(placebo_ids, rep(NA,sample_size-length(placebo_ids))))

```

Placebos - Event study for 2006:

```{r message=FALSE, warning=FALSE}
placebo_event_2006 <- data.frame(matrix(ncol = length(years_2006), nrow = ncol(placebo_samples)))
colnames(placebo_event_2006) <- years_2006

placebo_lead_names_2006 <- c("placebo:lead5","placebo:lead4", "placebo:lead3","placebo:lead2")

placebo_lag_names_2006 <- c("placebo:lag0","placebo:lag1","placebo:lag2","placebo:lag3","placebo:lag4",
                            "placebo:lag5","placebo:lag6","placebo:lag7","placebo:lag8","placebo:lag9","placebo:lag10")




for(i in 1:ncol(placebo_samples)){
  
  ids <- placebo_samples[,i]
  
  estim_data <- estim_data_all_2006 %>% filter(gbr == 0) %>% mutate(placebo = ifelse(id %in% ids, 1,0)) 
  
  event_placebo <- feols(IHS(loss) ~ placebo*(lead2 + lead3 + lead4 + lead5 + lag0 + lag1 + lag2 + lag3 + lag4 + 
                                           lag5 + lag6 + lag7 + lag8 + lag9 + lag10) + mintemp | 
                          id + year + region, 
                          data = estim_data, 
                          panel.id = ~id+year,
                          weights = ~prevcover)
  
  placebo_event_2006[i,1:length(years_2006)] <- c(summary(event_placebo)$coefficients[placebo_lead_names_2006],
                                                     0,
                                                     summary(event_placebo)$coefficients[placebo_lag_names_2006])
  
}


```

Placebos - Event Study for 2017:

```{r message=FALSE, warning=FALSE}
placebo_event_2017 <- data.frame(matrix(ncol = length(years_2017), nrow = ncol(placebo_samples)))
colnames(placebo_event_2017) <- years_2017

placebo_lead_names_2017 <- c("placebo:lead7", "placebo:lead6", "placebo:lead5","placebo:lead4",
                             "placebo:lead3","placebo:lead2")

placebo_lag_names_2017 <- c("placebo:lag0", "placebo:lag1","placebo:lag2","placebo:lag3","placebo:lag4")



for(i in 1:ncol(placebo_samples)){
  
  ids <- placebo_samples[,i]
  
  estim_data <- estim_data_all_2017 %>% filter(gbr == 0) %>% mutate(placebo = ifelse(id %in% ids, 1,0)) 
  
  event_placebo <- feols(IHS(loss) ~ placebo*(lead2 + lead3 + lead4 + lead5 + lead6 + lead7 + lag0 + lag1 + 
                                           lag2 + lag3 + lag4) + mintemp | id + year + region, 
                          data = estim_data, 
                          panel.id = ~id+year,
                          weights = ~prevcover)
  
  placebo_event_2017[i,1:length(years_2017)] <- c(summary(event_placebo)$coefficients[placebo_lead_names_2017],
                                                     0,
                                                     summary(event_placebo)$coefficients[placebo_lag_names_2017])
  
}


```


BMTAs - Event Study 2006:


```{r}
bmta_event_2006 <- data.frame(years_2006)
colnames(bmta_event_2006) <- "Year"


estim_data_bmta_2006 <- estim_data_all_2006 %>% filter(type %in% c("Control", "BMTA"))
  
event_bmta_2006 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lag0 + lag1 + lag2 + lag3 + lag4 + 
                                           lag5 + lag6 + lag7 + lag8 + lag9 + lag10) + mintemp | id + year + region, 
                          data = estim_data_bmta_2006, 
                          panel.id = ~id+year,
                          weights = ~prevcover)
  
bmta_event_2006 <- bmta_event_2006 %>% 
    mutate(Estimate_BMTA = c(summary(event_bmta_2006)$coefficients[coefficient_lead_names_2006],0,
                       summary(event_bmta_2006)$coefficients[coefficient_lag_names_2006]))
  

```


Hypothesis test:

```{r}

placebo_event_2006 %>% 
  pivot_longer(1:length(years_2006),names_to = "Year", values_to = "Estimate") %>% 
  mutate(Year = as.numeric(Year)) %>% 
  left_join(bmta_event_2006, by = "Year") %>% 
  ggplot() +
    geom_histogram(aes(x = Estimate), bins = 10, color = "lightseagreen", fill = "lightseagreen", alpha = 0.4) +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.05))) +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.95))) +
    geom_vline(aes(xintercept = Estimate_BMTA), linetype = "dashed") +
    facet_wrap(~Year, ncol = 4) +
    ylab("Count")


```
Parallel trends validated, but also no expectation of an effect in the DiD.

BMTAs and SFMAs - Event Study in 2017:

```{r message=FALSE, warning=FALSE}
zones <- c("BMTA", "SFMA")

bmta_sfma_event_2017 <- data.frame(years_2017)
colnames(bmta_sfma_event_2017) <- "Year"

for(i in zones){
  
  estim_data_2017 <- estim_data_all_2017 %>% filter(type %in% c("Control", i))
  
  event_2017 <- feols(IHS(loss) ~ gbr*(lead2 + lead3 + lead4 + lead5 + lead6 + lead7 + lag0 + lag1 + 
                                           lag2 + lag3 + lag4) + mintemp | id + year + region, 
                          data = estim_data_2017, 
                          panel.id = ~id+year,
                          weights = ~prevcover)
  
  
  bmta_sfma_event_2017 <- bmta_sfma_event_2017 %>% 
    mutate(!!paste0("Estimate_",i) := c(summary(event_2017)$coefficients[coefficient_lead_names_2017],0,
                       summary(event_2017)$coefficients[coefficient_lag_names_2017]))
  
}

```

And here is the result for SFMAs(this is Figure 7 in the paper):

```{r}

placebo_event_2017 %>% 
  pivot_longer(1:length(years_2017),names_to = "Year", values_to = "Estimate") %>% 
  mutate(Year = as.numeric(Year)) %>% 
  left_join(bmta_sfma_event_2017, by = "Year") %>% 
  ggplot() +
    geom_histogram(aes(x = Estimate), bins = 10, color = "orange2", fill = "orange2", alpha = 0.4) +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.05)), linetype = "dashed") +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.95)), linetype = "dashed") +
    geom_vline(aes(xintercept = Estimate_SFMA)) +
    #geom_vline(aes(xintercept = Estimate_BMTA), linetype = "dashed") +
    facet_wrap(~Year, ncol = 4) +
    ylab("Count") +
    theme_bw()

#ggsave("graphics/event_2017_sfma.png", height = 5, width = 8)
```

Parallel trends confirmed, yet likely no effect in the DiD.


Placebo - DiD 2006:


```{r message=FALSE, warning=FALSE}
placebo_did_2006 <- data.frame(matrix(ncol = 1, nrow = ncol(placebo_samples)))
colnames(placebo_did_2006) <- "Estimate"


for(i in 1:ncol(placebo_samples)){
  
  ids <- placebo_samples[,i]
  
  estim_data <- estim_data_all_2006 %>% filter(gbr == 0) %>% mutate(placebo = ifelse(id %in% ids, 1,0)) 
  
  did_2006 <- feols(IHS(loss) ~ placebo*post_2006 + mintemp | id + year + region, 
                              data = estim_data, panel.id = ~id+year,
                              weights = ~prevcover)
  

  placebo_did_2006[i,1] <- summary(did_2006)$coefficients["placebo:post_2006"]

}

```


Placebo -  DiD 2017


```{r message=FALSE, warning=FALSE}
placebo_did_2017 <- data.frame(matrix(ncol = 1, nrow = ncol(placebo_samples)))
colnames(placebo_did_2017) <- "Estimate"


for(i in 1:ncol(placebo_samples)){
  
  ids <- placebo_samples[,i]
  
  estim_data <- estim_data_all_2017 %>% filter(gbr == 0) %>% mutate(placebo = ifelse(id %in% ids, 1,0)) 
  
  did_2017 <- feols(IHS(loss) ~ placebo*post_2017 + mintemp | id + year + region, 
                              data = estim_data, panel.id = ~id+year,
                              weights = ~prevcover)
  

  placebo_did_2017[i,1] <- summary(did_2017)$coefficients["placebo:post_2017"]

}

```

BMTAs - DiD 2006:

```{r}
did_bmta_2006 <- feols(IHS(loss) ~ gbr*post_2006 + mintemp | id + year + region, 
                              data = estim_data_bmta_2006, panel.id = ~id+year,
                              weights = ~prevcover, cluster = "region")

bmta_coef_2006 <- summary(did_bmta_2006)$coefficients["gbr:post_2006"]


summary(did_bmta_2006)
```

Not even significant with clustering. Let's look at the result of the test:

```{r}
placebo_did_2006 %>% 
  ggplot()+
    geom_histogram(aes(x = Estimate), bins = 10, color = "lightseagreen", fill = "lightseagreen", alpha = 0.4) +
    geom_vline(aes(xintercept = bmta_coef_2006)) +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.05)), linetype = "dashed") +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.95)), linetype = "dashed") +
    ylab("Count")
```

BMTAs, SFMAs - DiD 2017

```{r message=FALSE, warning=FALSE}
estim_data_bmta_2017 <- estim_data_all_2017 %>% filter(type %in% c("Control", "BMTA"))


did_bmta_2017 <- feols(IHS(loss) ~ gbr*post_2017 + mintemp | id + year + region, 
                              data = estim_data_bmta_2017, panel.id = ~id+year,
                              weights = ~prevcover, cluster = "region")

bmta_coef_2017 <- summary(did_bmta_2017)$coefficients["gbr:post_2017"]

summary(did_bmta_2017)

estim_data_sfma_2017 <- estim_data_all_2017 %>% filter(type %in% c("Control", "SFMA"))


did_sfma_2017 <- feols(IHS(loss) ~ gbr*post_2017 + mintemp | id + year + region, 
                              data = estim_data_sfma_2017, panel.id = ~id+year,
                              weights = ~prevcover, cluster = "region")

sfma_coef_2017 <- summary(did_sfma_2017)$coefficients["gbr:post_2017"]


summary(did_sfma_2017)

```


So the BMTAs show no effect at all with clustering, SFMAs do when clustered (highly significant). Let's check if that holds with the placebo for the BMTAs:

```{r}
placebo_did_2017 %>% 
  ggplot()+
    geom_histogram(aes(x = Estimate), bins = 10, color = "lightseagreen", fill = "lightseagreen", alpha = 0.4) +
    geom_vline(aes(xintercept = bmta_coef_2017)) +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.05)), linetype = "dashed") +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.95)), linetype = "dashed") +
    ylab("Count")
```

And SFMAs (this is Figure 8):

```{r}
placebo_did_2017 %>% 
  ggplot()+
    geom_histogram(aes(x = Estimate), bins = 10, color = "orange2", fill = "orange2", alpha = 0.4) +
    geom_vline(aes(xintercept = sfma_coef_2017)) +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.05)), linetype = "dashed") +
    geom_vline(aes(xintercept = quantile(Estimate, probs = 0.95)), linetype = "dashed") +
    ylab("Count") +
    theme_bw()

ggsave("graphics/did_2017_sfma.png", height = 3, width = 5)
```

No effect.
