---
title: "Shapefile Creation"
output: html_notebook
---

Last update: 19.08.2023
Author: Peter Kamal (peter.kamal@t-online.de)

This notebook exists to create the shapefile that contains the observational units for DiD estimation. I include maps to make clear what is happening. First, we have to import all the data. Data comes from:

* Grid: https://catalogue.data.gov.bc.ca/dataset/bcgs-1-20-000-grid 
* Districts: https://catalogue.data.gov.bc.ca/dataset/regional-districts-legally-defined-administrative-areas-of-bc 
* GBR: https://catalogue.data.gov.bc.ca/dataset/fadm-special-protection-area 
* Land Use Zones: https://ebmdata.ca/download/GBR_Protected.gdb.zip 

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)

dataDir <- "C:/Users/Kamal/OneDrive/TSE/M2 EE/thesis/econ/data/shapefiles/"

grid <- st_read(paste0(dataDir,"20K_GRID_polygon_gcs.shp"))
districts <- st_read(paste0(dataDir,"ABMS_RD_polygon.shp"))
gbr <- st_read(paste0(dataDir,"FADM_SPA_polygon.shp")) %>% filter(DSGNTD_AR == "Great Bear Rainforest")
parks <- st_read(paste0(dataDir,"ParksER_GBR-polygon.shp"))
conservancies <- st_read(paste0(dataDir,"Cons_GBR_HG-polygon.shp"))
bmtas <- st_read(paste0(dataDir,"BMTA_GBR-polygon.shp"))
sfmas <- st_read(paste0(dataDir,"SFMA_GBR-polygon.shp"))

#vector of all coastal districts
coast_districts <- c("RDAC","CAPRD","CCRD","CMXRD","CVRD","FVRD","RDKS","MVRD",
                     "RDMW","RDN","NCRD","qRD","SLRD","STRD","SCRD")
```


This cuts down the districts and the grid to coastal BC:

```{r message=FALSE, warning=FALSE}
districts <- districts %>% filter(ABRVN %in% coast_districts)

grid <- st_transform(grid,st_crs(districts))

coast <- st_intersection(grid, districts)

coast <- coast %>% 
  select(OBJECTID, ABRVN,geometry)

ggplot() +
  geom_sf(data = coast, aes(fill = ABRVN)) +
  scale_fill_viridis_d(option = "mako")

```

This constructs a single shapefile that contains all sorts of protected areas within the GBR, and classifies non-protected areas as well. In doing so, it unifies the shape of the data first.

```{r message=FALSE, warning=FALSE}
bmtas <- bmtas %>% 
  select(BMTA_NAME,geometry) %>% 
  rename(Zone = BMTA_NAME) %>% 
  mutate(Type = "BMTA", .after = Zone)

conservancies <- conservancies %>% 
  select(CONSERVANC, geometry) %>% 
  rename(Zone = CONSERVANC) %>% 
  mutate(Type = "Conservancy", .after = Zone)

gbr <- gbr %>% 
  select(DSGNTD_AR, geometry) %>% 
  rename(Zone = DSGNTD_AR) %>% 
  mutate(Type = "GBR", .after = Zone)

parks <- parks %>% 
  select(PROTECTED_, PROTECTE_2, geometry) %>% 
  rename(Zone = PROTECTED_,
         Type = PROTECTE_2)

sfmas <- sfmas %>% 
  select(PROTECTE_1,PROTECTE_2, geometry) %>% 
  rename(Zone = PROTECTE_1,
         Type = PROTECTE_2)


all_protected <- dplyr::bind_rows(bmtas, conservancies,parks,sfmas)

all_protected_outline <- st_union(all_protected)

gbr_non_protected <- st_difference(gbr,all_protected_outline)

gbr_non_protected <- gbr_non_protected %>% 
  mutate(Type = "GBR - Not designated")

gbr_plus <- dplyr::bind_rows(all_protected,gbr_non_protected)

gbr_plus_outline <- st_union(gbr_plus)

ggplot() +
  geom_sf(data = gbr_plus, aes(fill = Type)) +
  scale_fill_viridis_d(option = "cividis")
```


This matches the land use zones to the grid.


```{r message=FALSE, warning=FALSE}
coast_gbr <- st_intersection(coast,gbr_plus)
coast_non_gbr <- st_difference(coast, gbr_plus_outline)

coast_gbr <- coast_gbr[st_is(coast_gbr, c("POLYGON", "MULTIPOLYGON")),]

coast_non_gbr <- coast_non_gbr %>% 
  mutate(Zone = "Coast - Non Protected",Type = "Control", .after = ABRVN)

coast_full <- dplyr::bind_rows(coast_gbr,coast_non_gbr)

ggplot()+
  geom_sf(data = coast_full, aes(fill = Type)) +
  scale_fill_viridis_d(option = "cividis")
```


This cleans the data up and saves it disaggregated by land use zone. This is necessary due to memory restrictions in the GEE API.

```{r}
coast_full <- coast_full %>% 
  cbind(1:4037) %>% 
  rename(ID = X1.4037, Region = ABRVN) %>% 
  select(-OBJECTID) %>% 
  relocate(ID, .before = Region) %>% 
  mutate(Type = case_when(Type == "ECOLOGICAL RESERVE" ~ "Ecological Reserve",
                          Type == "PROVINCIAL PARK" ~ "Provincial Park",
                          TRUE ~ Type)) 


outDir <- "C:/Users/Kamal/OneDrive/TSE/M2 EE/thesis/econ/data/satellite_input/v2/"

for(i in unique(coast_full$Type)){
  data <- coast_full %>%  filter(Type == i)
  st_write(data, paste0(outDir,i, ".shp"))
}

# Split the Control part in two to not exceed the memory:
control_part_one <- coast_full %>% 
  filter(Type == "Control") %>% 
  slice(1:974)

st_write(control_part_one, paste0(outDir,"control_part_one.shp"))

control_part_two <- coast_full %>% 
  filter(Type == "Control") %>% 
  slice(975:1874)

st_write(control_part_two, paste0(outDir,"control_part_two.shp"))

```


From here, these are individually ingested in the GEE JavaScript API, and exported as GEOJSONs using the script 'econ_3_satellite_raw_export.js'.

